---
output: rmarkdown::github_document
---
```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, fig.retina=2)
options(width=120)
```

# exiv

## Description

Read and Write 'Exif' Image Tags

### README FIRST!!! 

This package shld work on macOS and Linux systems that have the [`exiv2`](http://www.exiv2.org/) package installed.

- macOS: `brew install exiv2`
- Ubuntu/Debian `sudo apt-get install exiv2`

For the time being, it needs to be easily findable. It'll be more robust when the pkg is out of Alpha status.

ONLY "Standard" TAGS ARE SUPPORTED FOR THE MOMENT.
ONLY `ascii` TAGS ARE SUPPORTED FOR THE MOMENT. Full support for all tags will be here eventually

## What's Inside The Tin

The following functions are implemented:

- `read_exif`:	Retrieve Exif Data From An Image
- `set_exif`:	Set Exif tag data on an image file
- `exif_tags`:	Return a data frame of all possible Exif tags

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/exiv")
```

## Usage

```{r}
library(exiv)
library(tidyverse)

# current verison
packageVersion("exiv")
```

### Tags, you say?

We got your tags, _right here_:

```{r}
exif_tags(filter_type="ascii")
```

### Read exif data

This shld be an empty data frame:

```{r}
r_logo <- system.file("extdata", "Rlogo.png", package="exiv")

read_exif(r_logo)
```

Let's move it and add some ASCII metadata!

```{r}
tf <- tempfile(fileext=".png")
file.copy(r_logo, tf)

set_exif(tf, "Exif.Image.ProcessingSoftware", "The incredibly unassuming exiv R package!")
```

Just to prove we did it:

```{r}
read_exif(tf)
```

Can I have another, then?

```{r}
set_exif(tf, "Exif.Image.ImageDescription", "The R logo. Duh!")
```

There should be two now!

```{r}
read_exif(tf)
```


```{r include=FALSE}
unlink(tf)
```